Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism

### 2024-02-08 paper/main.tex
Review responses

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Bayesian regression facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  pdfkeywords={Bayesian inference, kinetic models of cell metabolism,
multiomics integration, ordinary differential equations, regulatory
anlaysis},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, enhanced]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{results-and-discussion}{%
\section{Results and Discussion}\label{results-and-discussion}}

@@

\begin{minipage}[t]{\linewidth}

{\centering

\raisebox{-\height}{

@@

}

}

@@

\end{figure}

\hypertarget{dataset-and-model-specification}{%
\subsection{Dataset and model
specification}\label{dataset-and-model-specification}}

@@

\hypertarget{posterior-inference}{%
\subsection{Posterior inference}\label{posterior-inference}}

@@

\end{figure}

\hypertarget{sec-laplace}{%
\subsubsection{Comparison with Laplace
approximation}\label{sec-laplace}}

@@

\end{figure}

\hypertarget{effect-of-missing-metabolite-concentration-measurements}{%
\subsection{Effect of missing metabolite concentration
measurements}\label{effect-of-missing-metabolite-concentration-measurements}}

@@

\end{figure}

\hypertarget{application-to-regulatory-understanding}{%
\subsection{Application to regulatory
understanding}\label{application-to-regulatory-understanding}}

@@

\end{figure}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{kinetic-model}{%
\subsection{Kinetic model}\label{kinetic-model}}

@@

\hypertarget{statistical-model}{%
\subsection{Statistical model}\label{statistical-model}}

@@

\hypertarget{bayesian-inference}{%
\subsubsection{Bayesian inference}\label{bayesian-inference}}

@@

\hypertarget{prior-model}{%
\subsubsection{Prior model}\label{prior-model}}

@@

\hypertarget{measurement-model}{%
\subsubsection{Measurement model}\label{measurement-model}}

@@

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

@@

\hypertarget{solving-the-steady-state-problem}{%
\subsection{Solving the steady state
problem}\label{solving-the-steady-state-problem}}

@@

\hypertarget{supporting-information}{%
\section{Supporting information}\label{supporting-information}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{author-information}{%
\section{Author information}\label{author-information}}

\hypertarget{author-contribution}{%
\subsection{Author contribution}\label{author-contribution}}

@@

Lars Keld Nielsen: Supervision, writing manuscript, designing
statistical model, biological model, software architecture and user
interface. \# References

\hypertarget{conflict-of-interest}{%
\subsection{Conflict of interest}\label{conflict-of-interest}}

@@

>>>>

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Bayesian regression facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  pdfkeywords={Bayesian inference, kinetic models of cell metabolism,
multiomics integration, ordinary differential equations, regulatory
anlaysis},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}

\section{Introduction}\label{introduction}

@@

\section{Results and Discussion}\label{results-and-discussion}

@@

\begin{minipage}{\linewidth}

@@

@@

\end{figure}%

\subsection{Dataset and model
specification}\label{dataset-and-model-specification}

@@

\subsection{Posterior inference}\label{posterior-inference}

@@

\end{figure}%

\subsubsection{Comparison with Laplace approximation}\label{sec-laplace}

@@

\end{figure}%

\subsection{Effect of missing metabolite concentration
measurements}\label{effect-of-missing-metabolite-concentration-measurements}

@@

\end{figure}%

\subsection{Application to regulatory
understanding}\label{application-to-regulatory-understanding}

@@

\end{figure}%

\section{Methods}\label{methods}

@@

\subsection{Kinetic model}\label{kinetic-model}

@@

\subsection{Statistical model}\label{statistical-model}

@@

\subsubsection{Bayesian inference}\label{bayesian-inference}

@@

\subsubsection{Prior model}\label{prior-model}

@@

\subsubsection{Measurement model}\label{measurement-model}

@@

\subsection{Implementation}\label{implementation}

@@

\subsection{Solving the steady state
problem}\label{solving-the-steady-state-problem}

@@

\section{Supporting information}\label{supporting-information}

@@

\section{Acknowledgements}\label{acknowledgements}

@@

\section{Author information}\label{author-information}

\subsection{Author contribution}\label{author-contribution}

@@

Lars Keld Nielsen: Supervision, writing manuscript, designing
statistical model, biological model, software architecture and user
interface.

\subsection{Conflict of interest}\label{conflict-of-interest}

@@

\section{References}\label{references}

### 2024-02-08 paper/supporting_information.qmd
Review responses

\begin{align} 
Saturation_r &= a \cdot \text{free enzyme ratio}\label{eq-saturation} \\ 
a &= \prod_{\text{s substrate}}\frac{C_{mic}^s}{k_{M}^{rs}} \nonumber \\ 
\text{free enzyme ratio} &= \begin{cases} 
  \prod_{\text{s sustrate}} (1 + \frac{C_{mic}^s}{k_{M}^{rs}})^{S_sr} 
  + \sum_{\text{c inhibitor}}\frac{C_{mic}^c}{k_I^{rc}} & r\text{ irreversible} \\ 
  -1 
  + \prod_{\text{s sustrate}} (1 + \frac{C_{mic}^s}{k_{M}^{rs}})^{S_sr} 
     + \sum_{\text{c inhibitor}}\frac{C_{mic}^c}{k_I^{rc}} 
     + \prod_{\text{p product}} (1 + \frac{C_{mic}^p}{k_{M}^{rp}})^{S_pr}  & r\text{ reversible} 
    \end{cases} \nonumber
\end{align}

>>>>

\begin{align} 
Saturation_r &= a \cdot \text{free enzyme ratio}\label{eq-saturation} \\ 
a &= \prod_{\text{s substrate}}\frac{C_{mic}^s}{k_{M}^{rs}} \nonumber \\ 
\text{free enzyme ratio} &= \begin{cases} \begin{aligned}
  &\prod_{\text{s sustrate}} (1 + \frac{C_{mic}^s}{k_{M}^{rs}})^{S_sr} \\
  + &\sum_{\text{c inhibitor}}\frac{C_{mic}^c}{k_I^{rc}}\end{aligned} & r\text{ irreversible} \\ 
  \begin{aligned}
  -1  &+ \prod_{\text{s sustrate}} (1 + \frac{C_{mic}^s}{k_{M}^{rs}})^{S_sr} \\
      &+ \prod_{\text{p product}} (1 + \frac{C_{mic}^p}{k_{M}^{rp}})^{S_pr} \\ 
      &+ \sum_{\text{c inhibitor}}\frac{C_{mic}^c}{k_I^{rc}} 
  \end{aligned}
    & r\text{ reversible} 
    \end{cases} \nonumber
\end{align}

### 2024-02-08 paper/supporting_information.tex
Review responses

\renewcommand{\thepage}{S\arabic{page}}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\title[]{Supporting information - Bayesian regression facilitates
quantitative modelling of cell metabolism}
\makeatletter
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, interior hidden, frame hidden, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\hypertarget{mauds-input-format}{%
\section{Maud's input format}\label{mauds-input-format}}

@@

\hypertarget{mauds-kinetic-model}{%
\section{Maud's kinetic model}\label{mauds-kinetic-model}}

\hypertarget{parameters}{%
\subsection{Parameters}\label{parameters}}

@@

\hypertarget{tbl-params}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4722}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2778}}@{}}
\caption{\label{tbl-params}Table S1 -- Parameters of Maud's statistical
model}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Modelled quantity
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimensions
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Modelled quantity
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimensions
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(\Delta_fG\) & Formation energy & metabolites \\
\(k_M\) & Michaelis Menten constants & Substrates of all
enzyme/reactions and products of reversible enzyme/reactions \\
\(k_I\) & Inhibition constants & Inhibiting metabolite/compartments of
enzyme/reactions exhibiting competitive inhibition \\
\(k_{cat}\) & Rate constants & Enzyme/reactions \\
\(L_0\) & Transfer constants & Allosteric interactions \\
\(e_T\) & T dissociation constants & Modifying metabolites of allosteric
inhibitions \\
\(e_R\) & R dissociation constants & Modifying metabolites of allosteric
activations \\
\(k_{cat\, pme}\) & Rate constants of phosphorylation modifying enzymes
& Phosphorylation modifying enzymes \\
\(v_{drain}\) & Drain fluxes & Drains, experiments \\
\(Enzyme\) & Enzyme concentrations & Enzymes, experiments \\
\(C_{unbalanced}\) & Unbalanced metabolite/compartment concentrations &
Unbalanced metabolite/compartments, experiments \\
\(C_{pme}\) & Phosphorylation modifying enzyme concentrations &
Phosphorylation modifying enzymes, experiments \\
\(\psi\) & Membrane potentials & Experiments \\
\end{longtable}

@@

\hypertarget{rate-equations}{%
\subsection{Rate equations}\label{rate-equations}}

@@

\hypertarget{sec-methionine-case-study}{%
\section{Methionine case study}\label{sec-methionine-case-study}}

\hypertarget{dataset-generation}{%
\subsection{Dataset generation}\label{dataset-generation}}

@@

\hypertarget{sec-methionine-priors}{%
\subsection{Prior distributions compared with true parameter
values}\label{sec-methionine-priors}}

@@

\hypertarget{tbl-case-study-params}{}

@@

\caption{\label{tbl-case-study-params}Table S2 -- Parameter
specification, marginal prior distributions and true parameter values
used in our case study.}\tabularnewline

@@

\hypertarget{computation}{%
\subsection{Computation}\label{computation}}

@@

\hypertarget{laplace-approximation-case-study}{%
\section{Laplace approximation case
study}\label{laplace-approximation-case-study}}

@@

\hypertarget{multimodal-posterior-distributions}{%
\section{Multimodal posterior
distributions}\label{multimodal-posterior-distributions}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

\renewcommand{\thepage}{S\arabic{page}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supporting information - Bayesian regression facilitates quantitative modelling of cell metabolism},
  pdfauthor={Teddy Groves; Nicholas Luke Cowie; Lars Keld Nielsen},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\title[]{Supporting information - Bayesian regression facilitates
quantitative modelling of cell metabolism}
\makeatletter
\begin{document}
\maketitle

@@

\section{Maud's input format}\label{mauds-input-format}

@@

\section{Maud's kinetic model}\label{mauds-kinetic-model}

\subsection{Parameters}\label{parameters}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4722}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2778}}@{}}
\caption{Table S1 -- Parameters of Maud's statistical
model}\label{tbl-params}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Modelled quantity
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimensions
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Modelled quantity
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Dimensions
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\(\Delta_fG\) & Formation energy & metabolites \\
\(k_M\) & Michaelis Menten constants & Substrates of all
enzyme/reactions and products of reversible enzyme/reactions \\
\(k_I\) & Inhibition constants & Inhibiting metabolite/compartments of
enzyme/reactions exhibiting competitive inhibition \\
\(k_{cat}\) & Rate constants & Enzyme/reactions \\
\(L_0\) & Transfer constants & Allosteric interactions \\
\(e_T\) & T dissociation constants & Modifying metabolites of allosteric
inhibitions \\
\(e_R\) & R dissociation constants & Modifying metabolites of allosteric
activations \\
\(k_{cat\, pme}\) & Rate constants of phosphorylation modifying enzymes
& Phosphorylation modifying enzymes \\
\(v_{drain}\) & Drain fluxes & Drains, experiments \\
\(Enzyme\) & Enzyme concentrations & Enzymes, experiments \\
\(C_{unbalanced}\) & Unbalanced metabolite/compartment concentrations &
Unbalanced metabolite/compartments, experiments \\
\(C_{pme}\) & Phosphorylation modifying enzyme concentrations &
Phosphorylation modifying enzymes, experiments \\
\(\psi\) & Membrane potentials & Experiments \\
\end{longtable}

@@

\subsection{Rate equations}\label{rate-equations}

@@

\section{Methionine case study}\label{sec-methionine-case-study}

\subsection{Dataset generation}\label{dataset-generation}

@@

\subsection{Prior distributions compared with true parameter
values}\label{sec-methionine-priors}

@@

@@

\caption{Table S2 -- Parameter specification, marginal prior
distributions and true parameter values used in our case
study.}\label{tbl-case-study-params}\tabularnewline

@@

\subsection{Computation}\label{computation}

@@

\section{Laplace approximation case
study}\label{laplace-approximation-case-study}

@@

\section{Multimodal posterior
distributions}\label{multimodal-posterior-distributions}

@@

\section{References}\label{references}
